Citation Analysis of Computer Science

### 2019-11-18 Scientometrics/comp.tex
edits to latex and bibtex, mainly focusing on low-level writing and text formtting

Given this powerful influence of computer science in research, some understanding its present state, structure, and relationship to other fields that goes beyond satisfying mere interest seems warranted since it would inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy. In using the term inform, we are mindful of (i) Greenhalgh (ii) Sarewitz and Pielke. \emph{I think that I want to cite these two without really knowing how. Greenhalgh for the limitations of positivism. Sarewitz for the limitations of allowing science to do whatever it wants to. I'd also like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study. I'm not sure where to put it though. CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007 } observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas. This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research. Maybe squeeze in Tandy's NAS report on interdisciplinarity. I should ping Ohid Yaqub about this too- science policy is his area.}

@@

In extending the work of Salton and Bergmark to the 21st century, we sought to combine journal and article based classifications in a scalable manner. Consequently, we used a whole text search method to match records from two major data sources. (i) the DBLP bibliography- a reference bibliography for computer science~\cite{dblp_ref} and  (ii) the journal-based Scopus bibliography, which more comprehensively covers the physical sciences, life sciences, social sciences, and health sciences. The underlying assumption is that a record in DBLP qualifies as computer science. Therefore, we cross-matched DBLP publications to Scopus to  enable identification of linked publications across multiple disciplines.

@@

\begin{figure}[ht]
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.2]{vlc.pdf}
% figure caption is below the figure
\caption{Schematic representation of variable clustering protocol modified from Small and Sweeney (1985). Three parameters are specified (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size. Input data is a set of co-cited publications with edge-weight defined by normalized co-citation frequencies. Green clusters are within the max cluster size. At the initial threshold, $t1$, a single cluster below the maximum cluster size, $mcs$ (green), along with one large cluster above it (red) are generated. As the threshold is incremented to $t2$, additional clusters of acceptable size is generated. The cascade continues to completion, which is defined by all clusters being of size less than or equal to the $mcs$. In this schematic, five rounds are adequate for the process to run to completion.}
\label{vlc_process}       % Give a unique label
\end{figure}

@@

For the purpose of this study, we defined, the computer science literature as a working set of all articles in the DBLP bibliography published in 1996-2015, that had a digital object identifier (DOI), and could be matched to article identifiers in the Scopus bibliography. The process of selection and matching resulted in a dataset of 634,100 publications (Materials and Methods). We constructed article level clusters of the computer science literature for the years 1996-2015, at a sufficiently high level of aggregation to be comparable to disciplinary classification by journal. Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}. Accordingly, we first used direct citation links as the basis for cluster formation. A set of 20 clusters was generated using a spectral clustering technique, Graclus, that has previously been applied to citation data~\cite{graclus_2007, subelj_clustering_2016}.  \emph{@sitaram please confirm the number of pubs that went into Graclus. I'm assuming it was 634,100?}. To place these clusters in context, we identified that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 minor subject areas in the Scopus ASJC classification. (which consists of 5 subject areas, 27 major subject areas, and 334 minor subject areas).

@@

\subsection{Subsection title}
\label{sec:2}
as required. Don't forget to give each section
and subsection a unique label (see Sect.~\ref{sec:1}).
\paragraph{Paragraph headings} Use paragraph headings as needed.
\begin{equation}
a^2+b^2=c^2
\end{equation}

>>>>

Given this powerful influence of computer science in research, some understanding its present state, structure, and relationship to other fields that goes beyond satisfying mere interest seems warranted since it would inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy. In using the term inform, we are mindful of (i) Greenhalgh (ii) Sarewitz and Pielke. \emph{I think that I want to cite these two without really knowing how. Greenhalgh for the limitations of positivism. Sarewitz for the limitations of allowing science to do whatever it wants to. I'd also like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study. I'm not sure where to put it though. CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007} observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas. This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research. Maybe squeeze in Tandy's NAS report on interdisciplinarity. I should ping Ohid Yaqub about this too- science policy is his area.}

@@

In extending the work of Salton and Bergmark to the 21st century, we sought to combine journal and article based classifications in a scalable manner. Consequently, we used a whole text search method to match records from two major data sources: (i) the DBLP bibliography--a reference bibliography for computer science~\cite{dblp_ref} and  (ii) the journal-based Scopus bibliography, which more comprehensively covers the physical sciences, life sciences, social sciences, and health sciences. 
\textcolor{blue}{Do we need to cite Scopus?}
The underlying assumption is that a record in DBLP qualifies as computer science. Therefore, we cross-matched DBLP publications to Scopus to  enable identification of linked publications across multiple disciplines.

@@

\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.2]{vlc.pdf}
% figure caption is below the figure
\caption{Schematic representation of variable clustering protocol modified from Small and Sweeney (1985). Three parameters are specified (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size. Input data is a set of co-cited publications with edge-weight defined by normalized co-citation frequencies. Green clusters are within the max cluster size. At the initial threshold, $t1$, a single cluster below the maximum cluster size, $mcs$ (green), along with one large cluster above it (red) are generated. As the threshold is incremented to $t2$, additional clusters of acceptable size is generated. The cascade continues to completion, which is defined by all clusters being of size less than or equal to the $mcs$. In this schematic, five rounds are adequate for the process to run to completion.}
\label{vlc_process}       % Give a unique label
\end{figure}

@@

For the purpose of this study, we defined, the computer science literature as a working set of all articles in the DBLP bibliography published in 1996-2015, that had a digital object identifier (DOI), and could be matched to article identifiers in the Scopus bibliography. The process of selection and matching resulted in a dataset of 634,100 publications (Materials and Methods). We constructed article level clusters of the computer science literature for the years 1996-2015, at a sufficiently high level of aggregation to be comparable to disciplinary classification by journal. Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}. Accordingly, we first used direct citation links as the basis for cluster formation. A set of 20 clusters was generated using a spectral clustering technique, Graclus, that has previously been applied to citation data~\cite{graclus_2007,subelj_clustering_2016}. 
\textcolor{blue}{
 \emph{@sitaram please confirm the number of pubs that went into Graclus. I'm assuming it was 634,100?}. 
 }To place these clusters in context, we identified that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 minor subject areas in the Scopus ASJC classification. (which consists of 5 subject areas, 27 major subject areas, and 334 minor subject areas).

@@

\subsection{Subsection title}
\label{sec:2}
as required. Don't forget to give each section
and subsection a unique label.
\paragraph{Paragraph headings} Use paragraph headings as needed.
\begin{equation}
a^2+b^2=c^2
\end{equation}
